% the acknowledgments section

\newthought{I am deeply grateful} to the many people who have made it possible for me be here today. First and foremost, thank you to my parents, who packed up their lives and moved to a foreign country, knowing neither the language nor the customs, so that my sisters and I could have the best possible life. Thank you for gifting us a world in which we believe anything is possible if we work hard and prepare for those moments when a bit of luck comes around. 

To my advisor, Dave, thank you for taking a chance on a weird Philosophy major. It has been a privilege to learn from you. You taught me so many fundamentals — what an Allen key is, how to solder, and how to not lose your mind (read: Github + virtual environments). In many ways you showed me how capable I am of creating something from nothing, which is one of the most valuable lessons I will take with me from grad school. 

To the NeuroEngineering crew (Ed, Joel, Brett, Adam, and technically, Max), thank you for helping me build realities from  vague ideas --- from not just one but three+ microscopes, to all the other weird rat-on-X devices I’ve conjured up over the years. Ed, you taught me almost everything I know about optics, debugging electrical noise, and perhaps most useful of all, how to use an oscilliscope. Thank you for the countless hours in which you patiently explained and re-explained basic lens concepts, and for never making me feel silly even after the 100th time I asked for help with the lasers. 

To my thesis committee (Jeff Lichtman, Mark Andermann, Venki Murthy), each one of you has gone above and beyond for me. Jeff, you have filled so many roles, from ombudsman to sage scientist — thank you for all the times you pushed me to be fearless and go for the big dreams like they are the only ones. Mark, you are one of my favorite people to talk about science with. Every chance to talk to you is a true privilege. But beyond that, you’ve believed in me so much, particularly when I believed in myself the least. You are vocal and active in pushing people like me to go for things, and I hope that one day I can become the scientist that you think I can be. Venki, there are few words to express how grateful I have been to feel like I have an ally out there. You are so thoughtful and kind, you always think of the small things that make all the difference in making someone feel welcome and supported. Though there have been difficult times in my PhD, I’ve been extremely fortunate to just be able to talk to you anytime. 

To Fanuel Muindi, Mike Lawrence, Patti, Lindsay Guest, and MCO --- thank you for supporting me and creating the fabric that makes up this department and program. So much of what you do is behind-the-scenes, answering frantic emails and desperate pleas of help. Thank you so much for your patience and enduring support, even when and especially when I was lab-less. 

To my lab, thanks for the fun times, especially Cesar, who worked through some of the toughest parts of grad school side-by-side with me (I will definitely miss the surgery beers, though not so much the surgeries). Thanks to extended lab friends, particularly Risa, who forced me to learn how to use a dissection scope and introduced me to amazing women in science. 

A huge thanks to Michael Cohen, George Alvarez, and Ken Nakayama of the Vision Sciences Lab, where I had one of the best lab experiences of my life, an experience that set me on the course I am on today. Michael, I am deeply and forever grateful to you for teaching me the literal fundamentals of science. From reading papers to forcing me to think of new experiment ideas, to teaching me about pivot tables, and then eventually, pushing me to code like George, you gave me the foundation for everything I do now. I was incredibly fortunate to have a mentor in you (and plus, kids house definitely had the best parties at VSS).

Thank you to my Cambridge/Boston family: from old friends to new, my many years here have made this my home (even converting me into a dreaded Boston sports fan, \#GoPats \#DoYourJob). Dhaka, you are my brother for life, thank you for believing in me when I was a silly girl and always expecting better but loving me at my worst. The OG Gorham crew (Gonzo, Tom, Zach), when the dirt hit the floor and crops needed to be watered into the wee hours of the morning, you were there to keep me sane the entire way. Thank you for supporting me in my extracurriculars and helping me to not take life so seriously. To the extended Gorham/karaoke crew (Matt, Rachel, Felix, Peter, Carmela), thank you for the sushi nights, bolognese nights, pretty much anything involving food, 90s crunk music, and Mariah. To the Old Folks (Peter, Felix, Carmela), thank you for being cranky and pessimistic with me in the shadows under some overhang and getting weird at Shay's. To the Boda Crew (James, Denise, Tom, Zach), thank you for literally pushing me to give all I got (and for admiring the bruises I have to show for it). To my awesome cohort, thanks for the fun times, the wonderfully useless hours of volleyball, masquerades, and drunken nights at our tiny apartments. 

To PMC crew (Julie L, Cindy, Yan, Michelle, Theresa, Alice, Nikki, Lisa),  we came together in solidarity and as allies to face a horrifying year that only seemed to get worse. You guys showed me the many faces and complexities of a human navigating turbulent worlds, both the smaller one within academia, and the world out there. Thank you for the strength, positive energy, hugs, and food envy, that has made what might have been the worst year into one of the best of my grad school years.

To Zach, you are my best friend, most daring partner-in-crime, and most productive collaborator. In one breath, you can make me laugh when things are super nicht gut, and in the next breath, walk through PCA with me. No matter how snowy the night, how cold the wind, or how horrible the 2AM p-set, everything is good so long as I'm with you and we've got some room-temperature beers. You are my favorite human being (Myshka is obviously my favorite creature). Thank you for being super awkward over purple corn drink and not letting me scare you away. x x


